% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% https://jblevins.org/projects/cv-template/
%
% Copyright (C) 2015-2019 Fredrik Savje
% https://fredriksavje.com
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}
%\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}

% Fonts
\usepackage[T1]{fontenc}
\usepackage[urw-garamond]{mathdesign}

% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {Fredrik Sävje},
	pdfkeywords = {Fredrik Sävje, Fredrik Savje, Curriculum Vitae, CV},
	pdftitle = {Fredrik Sävje: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

% Customize page headers
\pagestyle{myheadings}
\markright{Fredrik Sävje}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\large}
\subsectionfont{\rmfamily\mdseries\itshape\normalsize}

% Don't indent paragraphs.
\setlength\parindent{0em}

\newenvironment{datelist}{
	\begin{list}{}{
		\setlength{\parskip}{0pt}
		\setlength{\itemsep}{4pt}
		\setlength{\parsep}{0.3em}
		\setlength{\leftmargin}{5.85em}
		\setlength{\labelwidth}{5.85em}
		\setlength{\labelsep}{1.5em}
		}
	}{
\end{list}
}

\newenvironment{singledatelist}{
	\begin{list}{}{
		\setlength{\parskip}{0pt}
		\setlength{\itemsep}{4pt}
		\setlength{\parsep}{0.3em}
		\setlength{\leftmargin}{3.5em}
		\setlength{\labelwidth}{3.5em}
		\setlength{\labelsep}{1.5em}
		}
	}{
\end{list}
}

\newcommand{\dateitem}[2][]{\item[{#1}] {#2}}

\newenvironment{infolist}{
	\begin{list}{}{
		\setlength{\parskip}{0pt}
		\setlength{\itemsep}{4pt}
		\setlength{\parsep}{0.3em}
		\setlength{\leftmargin}{0em}
		\setlength{\labelwidth}{0em}
		}
	}{
\end{list}
}

\newcommand{\infoitem}[1]{\item {#1}}

\newenvironment{sublist}{
	\begin{list}{}{
		\setlength{\parskip}{0pt}
		\setlength{\itemsep}{0pt}
		\setlength{\parsep}{-0.25em}
		\setlength{\topsep}{0.1em}
		\setlength{\leftmargin}{2em}
		\setlength{\labelwidth}{0pt}
		}
	}{
\end{list}
}

\newcommand{\sublistitem}[1]{\begin{sublist}
		\item {\footnotesize {#1}}
	\end{sublist}}


\begin{document}

	{\huge \bf Fredrik Sävje}

	\rule{\textwidth}{1pt}

	\bigskip


	\begin{minipage}[t]{0.495\textwidth}
		Ekonomikum \\
		Kyrkogårdsgatan 10 \\
		Uppsala, Sweden
	\end{minipage}
	\begin{minipage}[t]{0.495\textwidth}
		\href{mailto:fredrik.savje@nek.uu.se}{\texttt{fredrik.savje@nek.uu.se}} \\
		\href{https://fredriksavje.com}{\texttt{https://fredriksavje.com}}
	\end{minipage}

	\vspace{0.3in}

	\section*{Current appointments \& affiliations}

	\begin{infolist}
		\infoitem{Associate Professor, Department of Economics, Uppsala University.}
		\infoitem{Docent, Department of Economics, Uppsala University.}
		\infoitem{Fellow, Uppsala Center for Fiscal Studies, Uppsala University.}
		\infoitem{Fellow, Institute for the Foundations of Data Science, Yale University.}
		\infoitem{Fellow, Institution for Social \& Policy Studies, Yale University.}
	\end{infolist}


	\section*{Past appointments}

	\begin{datelist}
		\dateitem[2023--2024]{Associate Professor (untenured), Department of Political Science, Yale University.}
		\dateitem[2023--2024]{Associate Professor (secondary), Department of Statistics \& Data Science, Yale University.}
		\dateitem[2017--2023]{Assistant Professor, Department of Political Science, Yale University.}
		\dateitem[2018--2023]{Assistant Professor (secondary), Department of Statistics \& Data Science, Yale University.}
		\dateitem[2015--2017]{Post-doctoral Fellow, Department of Political Science \& Department of Statistics, UC Berkeley.}
	\end{datelist}


	\section*{Education}

	\begin{singledatelist}
		\dateitem[2015]{Ph.D., Economics, Uppsala University.}
		\dateitem[2010]{B.Sc., Political Science \& Economics, Uppsala University.}
	\end{singledatelist}


	\section*{Publications}

	\subsection*{Peer-reviewed journal publications}

	\begin{infolist}
		\infoitem{Harshaw, Sävje, Spielman\ \& Zhang\ (2024).\ \href{https://doi.org/10.1080/01621459.2023.2285474}{Balancing Covariates in Randomized Experiments with the Gram–Schmidt Walk Design}.\ \textit{Journal of the American Statistical Association}, in print.}
		\infoitem{Sävje\ (2024).\ \href{https://doi.org/10.1093/biomet/asad019}{Causal inference with misspecified exposure mappings: separating definitions and assumptions}.\ \textit{Biometrika}, 111(1), 1--15.}
		\infoitem{Harshaw, Sävje, Eisenstat, Mirrokni\ \& Pouget-Abadie\ (2023).\ \href{https://doi.org/10.1214/23-EJS2111}{Design and analysis of bipartite experiments under a linear exposure-response model}.\ \textit{Electronic Journal of Statistics}, 17(1), 464--518.}
		\infoitem{Stommes, Aronow\ \& Sävje\ (2023).\ \href{https://doi.org/10.1177/20531680231166457}{On the reliability of published findings using the regression discontinuity design in political science}.\ \textit{Research \& Politics}, 10(2).}
		\infoitem{Sävje\ (2022).\ \href{https://doi.org/10.1093/biomet/asab035}{On the inconsistency of matching without replacement}.\ \textit{Biometrika}, 109(2), 551--558.}
		\infoitem{Sävje, Higgins\ \& Sekhon\ (2021).\ \href{https://doi.org/10.1017/pan.2020.32}{Generalized Full Matching}.\ \textit{Political Analysis}, 29(4), 423--447.}
		\infoitem{Sävje, Aronow\ \& Hudgens\ (2021).\ \href{https://projecteuclid.org/journals/annals-of-statistics/volume-49/issue-2/Average-treatment-effects-in-the-presence-of-unknown-interference/10.1214/20-AOS1973.short}{Average treatment effects in the presence of unknown interference}.\ \textit{Annals of Statistics}, 49(2), 673--701.}
		\infoitem{Delevoye\ \& Sävje\ (2020).\ \href{https://www.sciencedirect.com/science/article/pii/S0378375819301211}{Consistency of the Horvitz-Thompson estimator under general sampling and experimental designs}.\ \textit{Journal of Statistical Planning and Inference}, 207, 190--197.}
		\infoitem{Bengtsson, Sävje\ \& Swartling Peterson\ (2020).\ \href{https://onlinelibrary.wiley.com/doi/abs/10.1111/sjoe.12341}{Fetal iodine deficiency and schooling}.\ \textit{Scandinavian Journal of Economics}, 122(2), 582--621.}
		\infoitem{Higgins, Sävje\ \& Sekhon\ (2016).\ \href{https://www.pnas.org/content/113/27/7369}{Improving massive experiments with threshold blocking}.\ \textit{Proceedings of the National Academy of Sciences}, 113(27), 7369--7376.}
	\end{infolist}


	\subsection*{Invited and conference publications}

	\begin{infolist}
		\infoitem{Sävje\ (2024).\ \href{https://doi.org/10.1093/biomet/asad071}{Rejoinder: Causal inference with misspecified exposure mappings: separating definitions and assumptions}.\ \textit{Biometrika}, 111(1), 25--29.}
		\infoitem{Sävje\ (2021).\ \href{https://arxiv.org/abs/2107.14197}{Randomization does not imply unconfoundedness}.\ \textit{Workshop on the Neglected Assumptions in Causal Inference at ICML 2021}.}
		\infoitem{Sävje\ (2020).\ \href{https://projecteuclid.org/journals/statistical-science/volume-35/issue-3/Comment--Matching-Methods-for-Observational-Studies-Derived-from-Large/10.1214/19-STS739.short}{Comment: Matching Methods for Observational Studies Derived from Large Administrative Databases}.\ \textit{Statistical Science}, 35(3), 356--360.}
		\infoitem{Aronow\ \& Sävje\ (2020).\ \href{https://www.tandfonline.com/doi/full/10.1080/01621459.2020.1721245}{Review: The Book of Why}.\ \textit{Journal of the American Statistical Association}, 115(529), 482--485.}
	\end{infolist}


	\section*{Software}

	\begin{infolist}
		\infoitem{\href{https://github.com/crharshaw/GSWDesign.jl}{\texttt{GSWDesign.jl}}: Julia package with a fast implementation of the Gram-Schmidt Walk for balancing covariates in randomized experiments (also R wrapper).}
		\infoitem{\href{https://github.com/fsavje/distances}{\texttt{distances}}: R package with tools for distance metrics.}
		\infoitem{\href{https://github.com/fsavje/quickmatch}{\texttt{quickmatch}}: Quick Generalized Full Matching in R.}
		\infoitem{\href{https://github.com/fsavje/quickblock}{\texttt{quickblock}}: Quick Threshold Blocking in R.}
		\infoitem{\href{https://github.com/fsavje/scclust}{\texttt{scclust}}: C library for size-constrained clustering.}
	\end{infolist}


	\section*{Awards \& fellowships}

	\begin{infolist}
		\infoitem{Best Paper Award at 2022 NeurIPS Workshop on Causal Machine Learning for Real-World Impact, with Christopher Harshaw and Yitan Wang.}
		\infoitem{Yale Junior Faculty Fellowship, 2019--2020.}
		\infoitem{\href{https://www.cambridge.org/core/membership/spm/about-us/awards/the-gosnell-prize}{Gosnell Prize for Excellence in Political Methodology, 2018, with P. M. Aronow and Michael Hudgens}.}
	\end{infolist}


	\section*{Grants}

	\begin{infolist}
		\infoitem{Riksbankens Jubileumsfond, 2025--2027, SEK 3,122,255, as Co-PI with Christopher Harshaw.}
		\infoitem{NSF Methodology, Measurement, and Statistics Program, 2024--2027, USD 500,000, as Co-PI with Christopher Harshaw.}
		\infoitem{Planetary Solutions Project seed grant from the Climate Impact Innovation Fund and the Gordon Data and Environmental Sciences Research Grants, 2023--2024, USD 80,000, as Co-PI with Megan Ayers and Luke Sanford.}
		\infoitem{Swedish International Development Cooperation Agency, 2013--2015, SEK 2,595,000, with Niklas Bengtsson, Eva Mörk (PI) and Jonas Poulsen.}
		\infoitem{The Jan Wallander and Tom Hedelius foundation, 2013--2014, SEK 321,000.}
	\end{infolist}


	\section*{Research visits}

	\begin{datelist}
		\dateitem[2024]{Data Science Lab, Hertie School. 2 weeks.}
		\dateitem[2024]{Department of Economics, European University Institute. 2 weeks.}
		\dateitem[2024]{Department of Mathematical Sciences, University of Copenhagen. 3 weeks.}
		\dateitem[2024]{Harvard Data Science Initiative, Harvard University. 4 weeks.}
		\dateitem[2023]{Department of Political Science, University of Chicago. 6 weeks.}
		\dateitem[2019--2020]{Department of Political Science \& Graduate School of Business, Stanford University. Full AY.}
		\dateitem[2013--2014]{Department of Economics, UC Berkeley. Full AY.}
	\end{datelist}


	\section*{Presentations}

	\subsection*{Invited presentations}

	\begin{singledatelist}
		\dateitem[2025]{Statistical Laboratory, University of Cambridge, scheduled.}
		\dateitem[2024]{Data Science Lab, Hertie School.}
		\dateitem{Department of Economics, European University Institute.}
		\dateitem{Department of Mathematical Sciences, University of Copenhagen.}
		\dateitem{Department of Quantitative Theory and Methods, Emory University.}
		\dateitem{Harvard Data Science Initiative, Harvard University.}
		\dateitem[2023]{Methodology, Organization, and Management Workshop, Harvard Business School.}
		\dateitem{International Conference on Design of Experiments, University of Memphis.}
		\dateitem{Applied Statistics Workshop, Harvard University.}
		\dateitem{Ben Recht's Lab, UC Berkeley.}
		\dateitem{Department of Economics, Yale University.}
		\dateitem[2021]{Department of Economics, Rutgers University.}
		\dateitem{Econometrics and Statistics Colloquium, University of Chicago Booth School of Business.}
		\dateitem{Department of Political Science, NYU.}
		\dateitem{Department of Statistics, Stanford.}
		\dateitem{Cowles Foundation, New Haven.}
		\dateitem{Online Causal Inference Seminar, Stanford.}
		\dateitem[2020]{Department of Political Science, UC San Diego.}
		\dateitem{Interdisciplinary Seminar in Quantitative Methods, University of Michigan.}
		\dateitem{Gillings School of Global Public Health, UNC Chapel Hill.}
		\dateitem{Causal Inference Group, UC Berkeley.}
		\dateitem[2019]{Causal Learning with Interactions Conference, Cemmap, London.}
		\dateitem{Causal Inference Group, Stanford University.}
		\dateitem{Joint Statistical Meetings, Denver.}
		\dateitem[2018]{Joint Statistical Meetings, Vancouver.}
		\dateitem{Yamakawa Kenjiro Lecture, University of Tokyo.}
		\dateitem{European Causal Inference Meeting, University of Florence.}
		\dateitem{Department of Political Science, NYU.}
		\dateitem{Department of Political Science, MIT.}
		\dateitem[2016]{Columbia Business School, Columbia University.}
		\dateitem[2015]{Department of Political Science, Yale University.}
		\dateitem{Department of Statistics, Uppsala University.}
		\dateitem{Institute for International Economic Studies, Stockholm University.}
		\dateitem[2014]{Quantitative Methodology in the Social Sciences Seminar, UC Berkeley.}
		\dateitem{Department of Economics, Uppsala University.}
		\dateitem[2013]{Department of Statistics, Umeå School of Business and Economics.}
		\dateitem[2012]{Department of Economics, Uppsala University.}
	\end{singledatelist}


	\subsection*{Contributed presentations}

	\begin{singledatelist}
		\dateitem[2023]{Society for Political Methodology (PolMeth), Stanford University.}
		\dateitem{American Causal Inference Conference, UT Austin.}
		\dateitem[2022]{CMStatistics, London.}
		\dateitem{Latin American PolMeth, University of San Andrés.}
		\dateitem{Society for Political Methodology (PolMeth), Washington University.}
		\dateitem{American Causal Inference Conference, UC Berkeley.}
		\dateitem[2021]{APSA Annual Meeting, Seattle.}
		\dateitem{Society for Political Methodology, New York University.}
		\dateitem[2020]{Society for Political Methodology, University of Toronto.}
		\dateitem[2019]{Society for Political Methodology, MIT.}
		\dateitem{Atlantic Causal Inference Conference, McGill University.}
		\dateitem[2018]{APSA Annual Meeting, Boston.}
		\dateitem[2017]{Society for Political Methodology, University of Wisconsin-Madison.}
		\dateitem{Atlantic Causal Inference Conference, University of North Carolina.}
		\dateitem{Midwest Political Science Association, Chicago.}
		\dateitem[2016]{Midwest Political Science Association, Chicago.}
		\dateitem[2015]{Society for Political Methodology, University of Rochester.}
		\dateitem{UK Causal Inference Meeting, University of Bristol.}
		\dateitem[2013]{Uppsala Center for Labor Studies, Uppsala University.}
		\dateitem{Nordic Econometric Meeting, Norwegian School of Economics.}
	\end{singledatelist}


	\subsection*{Presentations as discussant}

	\begin{singledatelist}
		\dateitem[2023]{Society for Political Methodology, Stanford.}
		\dateitem[2022]{Latin American PolMeth, University of San Andrés.}
		\dateitem{Online Causal Inference Seminar, Stanford.}
		\dateitem[2021]{Society for Political Methodology, New York University.}
		\dateitem{Online Causal Inference Seminar, Stanford.}
		\dateitem[2020]{Society for Political Methodology, University of Toronto.}
		\dateitem[2019]{Society for Political Methodology, MIT.}
		\dateitem[2017]{Midwest Political Science Association, Chicago.}
	\end{singledatelist}


	\section*{Teaching}

	\subsection*{Uppsala University}

	\begin{infolist}
		\infoitem{Econometrics I (grad). Fall 2024.}
		\infoitem{Econometric Theory (master). Spring 2025.}
	\end{infolist}

	\subsection*{Yale University}

	\begin{infolist}
		\infoitem{Data Science for Politics and Policy (undergrad). Spring 2018, 2019, 2021, 2022.}
		\infoitem{Causal Inference and Research Design (grad). Spring 2021, Fall 2021, 2022.}
		\infoitem{Foundations of Statistical Inference (grad). Spring 2019, Fall 2020, 2021, 2022.}
		\infoitem{Advanced Quantitative Methods (grad). Fall 2017, 2018.}
		\infoitem{The Application of Quantitative Methods (grad). Spring 2018.}
	\end{infolist}


	\section*{Students}

	\subsection*{Dissertation committee chair}

	\begin{infolist}
		\infoitem{Amanda Weiss, Political Science, Yale, current.}
		\infoitem{Megan Ayers, Statistics, Yale, current.}
	\end{infolist}

	\subsection*{Dissertation committee member}

	\begin{infolist}
		\infoitem{Brandon Chow, Statistics, Yale, 2023.
			Placement: Microsoft.}
		\infoitem{\href{http://www.chrisharshaw.com/}{Chris Harshaw}, Computer Science, Yale, 2022.
			Placement: MIT \& UC Berkeley (post doc), Columbia (AP).}
		\infoitem{\href{https://kylepeyton.github.io}{Kyle Peyton}, Political Science, Yale, 2020.
			Placement: Australian Catholic University.}
		\infoitem{\href{https://mollyow.github.io}{Molly Offer-Westort}, Political Science and Statistics, Yale, 2019.
			Placement: Stanford (post doc), U Chicago (AP).}
	\end{infolist}

	\subsection*{Dissertation grading committee member}

	\begin{infolist}
		\infoitem{Mohammad Ghasempour, Umeå University, 2024.}
		\infoitem{Lilla Orr, Yale University, 2021.}
		\infoitem{John Ternovski, Yale University, 2021.}
		\infoitem{Costanza Tortù, IMT School for Advanced Studies Lucca, 2020.}
	\end{infolist}

	\subsection*{Dahl Research Scholar mentor}

	\begin{infolist}
		\infoitem{Akhil Rajan, Political Science, Yale, 2018--2019.}
	\end{infolist}


	\section*{Service}

	\subsection*{Uppsala University}

	\begin{infolist}
		\infoitem{Subfield Coordinator, Econometrics, 2024--2025.}
		\infoitem{Member of Department Board, 2024--2025.}
	\end{infolist}

	\subsection*{Yale University}

	\begin{infolist}
		\infoitem{Graduate Admissions Committee, 2020--2021, 2022--2023.}
		\infoitem{Quantitative Methods General Exam Committee, 2019, 2020, 2021, 2022.}
		\infoitem{Organizer, MacMillan--CSAP Workshop on Quantitative Research Methods, 2018, 2019, 2021, 2022, 2023.}
		\infoitem{Social Science--Data Science Search Committee, 2018.}
	\end{infolist}

	\subsection*{Disciplinary Service}

	\begin{infolist}
		\infoitem{Ad-hoc reviewer, Banff International Research Station, 2024.}
		\infoitem{Ad-hoc reviewer, National Science Foundation, 2021, 2022.}
		\infoitem{Committee member, Gosnell Prize for Excellence in Political Methodology, 2019.}
		\infoitem{Reviewer, American Statistical Association Biometrics Section Travel Awards, 2018.}
		\infoitem{Session organizer, Joint Statistical Meetings, 2018, 2023.}
	\end{infolist}

	\subsection*{Reviewer}

	\begin{infolist}
		\infoitem{American Journal of Political Science; American Political Science Review; American Statistician; Annals of Applied Statistics; Annals of Statistics; Biometrics; Biometrika; Biostatistics; Canadian Journal of Statistics; Communications in Statistics - Theory \& Methods; Econometrica; Electronic Journal of Statistics; European Journal of Political Economy; Journal of the American Statistical Association; Journal of Business \& Economic Statistics; Journal of Causal Inference; Journal of Computational and Graphical Statistics; Journal of Econometrics; Journal of Economic Behavior \& Organization; Journal of Health Economics; Journal of Machine Learning Research; Journal of the Royal Statistical Society: Series A; Journal of the Royal Statistical Society: Series B; Management Science; Political Analysis; Political Science Research \& Methods; The R Journal; Review of Economic Studies; Review of Economics and Statistics; Statistics \& Probability Letters; Statistics \& Public Policy.}
	\end{infolist}

	\bigskip
	{\small Last updated \today.}

\end{document}
